---
title: "JRB's Yoga"
author: "JRB"
date: "`r Sys.Date()`"


output: 
  html_document:
  flexdashboard::flex_dashboard:
    name: "jrb_yoga"
    output_dir: docs
    theme:
      #version: 4
      bg: "#484848"
      fg: "#FDF7F7" 
      primary: "#484848"
      navbar-bg: "#2e4263"
      base_font: 
        google: Prompt
      heading_font:
        google: Sen
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: JetBrains Mono
          local: false
    vertical_layout: scroll
runtime: shiny

---

```{r global, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = F)

library(flexdashboard)
library(readr)
library(leaflet)
library(DT)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggplot2)
library(knitr)
library(shiny)
library(DT)
library(wesanderson)
library(ggmap)
library(tidyr)
library(dplyr)
library(sp)
library(rgdal)
library(jsonlite)
library(maptools)
library(ggthemes)
library(scales)
library(MASS)
library(viridis)
library(reshape2)
library(RColorBrewer)
library(leaflet.extras)
library(raster)
library(RColorBrewer)
library(leaflet.esri)
library(tigris)
library(hrbrthemes)

yoga <-
  read.csv(
    "/Users/jrb/Desktop/R/yoga.csv",
    row.names = NULL,
    sep = ","
  )

# format variables:
yoga$watch_time <- hms(yoga$watch_time, quiet = T)
yoga$hour <- hms("01:00:00", quiet = T)
yoga$hour_calories <- (yoga$calories * yoga$hour)/yoga$watch_time
yoga$date <- mdy(yoga$date)
yoga$day <- as.factor(yoga$day)
yoga$day <- factor(yoga$day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
yoga$time <- as.factor(yoga$time)
yoga$month_year <- format(as.Date(yoga$date), "%Y-%m")
yoga$Teacher <- gsub(" .*", "", yoga$teacher)

# event variables:
covid_width <- as.numeric(difftime(ymd("2022-01-14"), ymd("2021-12-27"), units = "days"))
surgery_width = as.numeric(difftime(ymd("2022-06-15"), ymd("2022_05_13"), units = "days"))

```

### Average Total Classes Heart Rate by Teacher: shape-size increases by number of classes with a teacher
    
```{r, fig.width= 14, fig.height= 8, warning=FALSE}
# average lifetime heart rate by teacher:
yoga %>%
  drop_na(avg_heart_rate) %>%
  group_by(Teacher) %>%
  mutate(teacher_count = length(Teacher)) %>%
  mutate(avg_heart = mean(avg_heart_rate)) %>%
  distinct(Teacher, .keep_all = T) %>%
  ggplot(
  aes(
    x = Teacher,
    y = avg_heart,
    label = avg_heart,
    fill = hour_calories,
    size = teacher_count
  )
) +
  coord_flip() +
  geom_point(alpha=0.85, shape=22, color="black", aes(size = teacher_count), fill = "#277F8EFF") +
  scale_size(range = c(5, 30)) +
  #scale_fill_viridis(discrete=F, guide="none", option="G") +
    theme_ipsum(grid = F) +
  theme(legend.position="none", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe")) +
  ylab("Average Heart Rate") +
  xlab("Teacher") +
  theme(plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10))
```
    
### Individual Class Calories by Teacher: shape-size increases with class average heart rate

```{r, fig.width= 14, fig.height= 8, warning=FALSE}
# Individual class calories per hour by teacher:
yoga %>%
  arrange(desc(hour_calories)) %>%
  ggplot(aes(
    x = hour_calories,
    y = Teacher,
    size = avg_heart_rate,
    fill = avg_heart_rate
  )) +
  geom_point(alpha = 0.5,
             shape = 21,
             color = "black") +
  scale_size(range = c(.1, 20)) +
  scale_fill_viridis(discrete = F,
                     guide = "none",
                     option = "A") +
  theme_ipsum(grid = F) +
  theme(
    legend.position = "none",
    axis.title.x = element_text(colour = "#bebebe") ,
    axis.title.y = element_text(colour = "#bebebe")
  ) +
  ylab("Teacher") +
  xlab("Calories per Hour") +
  theme(
    plot.background = element_rect(fill = "#484848"),
    axis.text.x = element_text(
      angle = 90,
      vjust = 1,
      hjust = 1,
      color = "#BEBEBE"
    ),
    axis.text.y = element_text(color = "#BEBEBE"),
    legend.text = element_text(colour = "#BEBEBE", size = 10)
  )
```

### Heart Rate by Individual Class

```{r, eval=T, fig.width= 14, fig.height= 8, warning=FALSE}
# Calories per class by individual date:
ggplot(
  data = yoga,
  aes(
    x = date,
    y = avg_heart_rate,
    label = avg_heart_rate,
    fill = avg_heart_rate
    #size = hour_calories
  )
) +
  # centering over start date:
  #geom_vline(xintercept = (ymd("2021-12-27") + (.5*covid_width)), lwd = covid_width, colour = "grey", alpha = .1) +
  geom_vline(xintercept = (ymd("2021-12-27") + (.5*covid_width)), lwd = 1, colour = "#c0369d", alpha = .7) +
  annotate("text", x=ymd("2021-12-27") + (.5*covid_width), y=90, label="COVID Diagnosis", angle=90, color = "white") +
  geom_vline(xintercept = (ymd("2022-05-13") + (.5*surgery_width)), lwd = surgery_width, colour = "grey", alpha = .1) +
  annotate("text", x=ymd("2022-05-13") + (.5*surgery_width), y=90, label="Wrist Surgeries", angle=90, color = "white") +
  geom_point(alpha=0.5, shape=21, color="black", size = 10) +
  #geom_smooth(method=lm, se=FALSE, color = "#C0369D", alpha = .7) +
  #scale_size(range = c(2, 10)) +
  scale_y_continuous(limits = c(80, 130)) +
  scale_fill_viridis(discrete=F,  option="A") +
  theme_ipsum(grid = F) +
  theme(legend.position="none", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe")) +
  ylab("Class Average Heart Rate") +
  xlab("Date") +
  theme(plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10)) 
```

### Calories by Individual Class

```{r, eval=T, fig.width= 14, fig.height= 8, warning=FALSE}
# Calories per class by individual date:
ggplot(
  data = yoga,
  aes(
    x = date,
    y = hour_calories,
    label = hour_calories,
    fill = hour_calories
    #size = hour_calories
  )
) +
  # centering over start date:
  geom_vline(xintercept = (ymd("2021-12-27") + (.5*covid_width)), lwd = 1, colour = "#c0369d", alpha = .7) +
  annotate("text", x=ymd("2021-12-27") + (.5*covid_width), y=130, label="COVID Diagnosis", angle=90, color = "white") +
  geom_vline(xintercept = (ymd("2022-05-13") + (.5*surgery_width)), lwd = surgery_width, colour = "grey", alpha = .1) +
  annotate("text", x=ymd("2022-05-13") + (.5*surgery_width), y=130, label="Wrist Surgeries", angle=90, color = "white") +
  #geom_smooth(method=lm, se=FALSE, color = "#C0369D", alpha = .5) +
  geom_point(alpha=0.5, shape=21, color="black", size = 10) +
  #scale_size(range = c(2, 10)) +
  scale_y_continuous(limits = c(85, 320)) +
  scale_fill_viridis(discrete=F,  option="A") +
  theme_ipsum(grid = F) +
  theme(legend.position="none", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe")) +
  ylab("Calories") +
  xlab("Date") +
  theme(plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10)) 
```

### Calories by Days of the Week: shape-size increases for count of classes that weekday

```{r, eval=T, fig.width= 14, fig.height= 8, warning=FALSE}
# days of the week:
yoga %>%
  drop_na(avg_heart_rate) %>%
  group_by(day) %>%
  mutate(Average_Heart_Rate_Day = mean(avg_heart_rate)) %>%
  mutate(Average_Calories_day = mean(hour_calories)) %>%
  mutate(day_count = length(day)) %>%
  distinct(day, .keep_all = T) %>%
  ggplot(
  aes(
    x = day,
    y = Average_Calories_day,
    label = Average_Calories_day,
    fill = Average_Calories_day,
    size = day_count,
  )
) +
  geom_point(shape=22, color="black", fill = "#277F8EFF") +
  scale_size(range = c(5, 30)) +
  #scale_fill_viridis(discrete=F,  option="G") +
  theme_ipsum(grid = F) +
  theme(legend.position="none", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe")) +
  ylab("Average Calories/Hour by Day") +
  xlab("Day") +
  theme(plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10)) 
```

### Average Heart Rate per Month: shape-size increases for number of classes that month

```{r, eval=T, fig.width= 14, fig.height= 8, warning=FALSE}
# Average class calories per month:
yoga %>%
  drop_na(avg_heart_rate) %>%
  group_by(month_year) %>%
  mutate(month_avg_heart = mean(avg_heart_rate)) %>%
  mutate(Count = length(month_year)) %>%
  distinct(month_year, .keep_all = T) %>%
  ggplot(
    aes(
    x = month_year,
    y = month_avg_heart,
    fill = month_avg_heart,
    size = Count
  )) +
  # make this month_year, not ymd:
  #geom_vline(xintercept = (ymd("2021-12-27") + (.5*covid_width)), lwd = 1, colour = "#c0369d", alpha = .7) +
  #annotate("text", x=ymd("2021-12-27") + (.5*covid_width), y=90, label="COVID Diagnosis", angle=90, color = "white") +
  geom_point(shape=21, color="black") +
  scale_size(range = c(5, 25)) +
  scale_fill_viridis(discrete=F,  option="G", guide = "none") +
  theme_ipsum(grid = F) +
  theme(legend.position="none", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe")) +
  ylab("Average Calories/Hour") +
  xlab("Date") +
  theme(plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10)) 
```

### Class Calories by Class Average Heart Rate

```{r, eval=T, fig.width= 14, fig.height= 8, warning=FALSE, message=FALSE}
ggplot(
  data = yoga
) +
  #calories:
  geom_point(aes(x = date, y = hour_calories, fill = "#C7C07A"), shape = 21, size = 10, alpha = .5) +
  geom_smooth(aes(x = date, y = hour_calories, fill = "#C7C07A"), method=lm, se=FALSE, alpha = .5) +
  # heart rate:
  geom_point(aes(x = date, y = avg_heart_rate, fill = "#69A1B4"), shape = 21, size = 10, alpha = .5) +
  geom_smooth(aes(x = date, y = avg_heart_rate, fill = "#69A1B4"), method=lm, se=FALSE, alpha = .5) +
  theme_ipsum(grid = F) +
  theme(legend.position="bottom", axis.title.x=element_text(colour="#bebebe") , axis.title.y=element_text(colour="#bebebe"), plot.background = element_rect(fill = "#484848"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1, color = "#BEBEBE"), axis.text.y = element_text(color = "#BEBEBE"), legend.text = element_text(colour="#BEBEBE", size = 10)) +
  xlab("Date") +
  ylab("Heart Rate / Calories") +
  scale_fill_manual(values = c("#C7C07A", "#69A1B4"), labels = c("Heart Rate", "Calories")) +
  guides(fill=guide_legend(title=""))

```
